On the minimum leaf conductance: its role in models of plant water use, and ecological and environmental controls

### 2018-02-15 manuscript.Rmd
references cleanup

\
Plants face a dilemma in constructing leaves that minimize water loss while allowing the uptake of CO~2~. Since a membrane that is permeable to CO~2~ but not H~2~O has never evolved, all land plants have stomata in their leaves, which disrupt the cuticle and allow CO~2~ uptake. It is well known that stomatal open and close in response to changes in light intensity, humidity and CO~2~ concentration at the leaf surface. In doing so, stomata can be thought to balance the uptake of CO~2~ with the loss of water, and thus can be expected to close stomata when photosynthetic rates are low. To avoid desiccation and ultimate death, stomata can also be expected to close during periods of severe water stress. When stomata are closed, water loss continues at a greatly diminished rate through the cuticle. After accounting for evaporative demand, this rate of water loss is expressed as the minimum conductance of a leaf. There is increasing recognition that the minimum conductance plays an important role in estimating water fluxes in plant canopies [@barnard2013], during heat waves [@kala2016], and in models of plant drought response [@blackman2016; @martinstpaul2017].

@@

**Methods S1** Literature compilation of g~min~ estimates
**Methods S2** Methodological issues with measurement of g~min~
**Methods S3** Methods description for case studies
**Table S1** Effects of drought stress on g~min~
**Figure S1** Effects of leaf age on g~min~

>>>>

\
Plants face a dilemma in constructing leaves that minimize water loss while allowing the uptake of CO~2~. Since a membrane that is permeable to CO~2~ but not H~2~O has never evolved, all land plants have stomata in their leaves, which disrupt the cuticle and allow CO~2~ uptake. It is well known that stomata open and close in response to changes in light intensity, humidity and CO~2~ concentration at the leaf surface. In doing so, stomata can be thought to balance the uptake of CO~2~ with the loss of water, and thus can be expected to close stomata when photosynthetic rates are low. To avoid desiccation and ultimate death, stomata can also be expected to close during periods of severe water stress. When stomata are closed, water loss continues at a greatly diminished rate through the cuticle. After accounting for evaporative demand, this rate of water loss is expressed as the minimum conductance of a leaf. There is increasing recognition that the minimum conductance plays an important role in estimating water fluxes in plant canopies [@barnard2013], during heat waves [@kala2016], and in models of plant drought response [@blackman2016; @martinstpaul2017].

@@

**Methods S1** Literature compilation of g~min~ estimates

**Methods S2** Methodological issues with measurement of g~min~

**Methods S3** Methods description for case studies

**Table S1** Effects of drought stress on g~min~

**Figure S1** Effects of leaf age on g~min~
